---
title: "Group 18 Final Project: Data Check"
author: "Omer Canca, Riley Blake, ZiyuanYe"
date: "November 10 2021"
output: html_notebook
---


```{r}
# Load `tidyverse` and `dcData` packages
rm(list = ls())     # clean up your R environment

# load packages
library(tidyverse) 
library(dplyr)
library(rvest)
```


### Data Source: 

Primary Data Source: obtained from kaggle - Sample of Car Data including multiple variables of car

URL: https://www.kaggle.com/jingbinxu/sample-of-car-data

```{r}
Cars <- read.csv("car_data.csv")
```

```{r}
head(Cars)
```
```{r}
tail(Cars)
```
```{r}
summary(Cars)
```

```{r}
glimpse(Cars)
```

### Examine the data source
* report what you know (or don't know) about who/what/when/where/why/how the data were originally collected (note: this is NOT about how you found it, etc): The dataset looks straightforward and tidy. 

* choose a few (3-4) key variables to describe (variable types, coding, missingness, summary statistics/plots): There are 205 cases with 23 variables. Each case represents a type of car and its attributes. The key attributes we are looking for are "make", "prices", "engine_size","engine_type", and so on. For example, make states the manufacture of the car, which is a categorical variable. engine_size demonstrates the engine size of a car in inch, which is a numerical attribute. The price is also a numerical attribute in dollars.

### Research Question: What are the key factors that can impacts the price of vehicles?














 

















