
---
title: "Activity: Bird Species"
author: "Ziyuan Ye"
date: "October 12 2021"
output: html_notebook
---


# Set Up

```{r}
# Load `tidyverse` and `DataComputing` packages

library(dcData)
library(tidyverse)  

# Load the `OrdwayBirds` data set into your RStudio environment from the `DataCompupacting` package

data("OrdwayBirds")

# Show a few commands used to inspect the data set a few different ways

View(OrdwayBirds)

```

### Step 0

```{r}
# Get the data table & clean up dates (see Data Computing eBook)
  OrdwayBirdsnew <-
  OrdwayBirds %>%
  select( SpeciesName, Month, Day ) %>%
  mutate( Month = as.numeric(as.character(Month)), 
          Day = as.numeric(as.character(Day)))
# Inspect resulting data
View(OrdwayBirdsnew)
```



### Step 1
```{r}
# unique species in original data (including mis-spellings)
OrdwayBirds %>%
  summarise(count = n_distinct(SpeciesName))
```


```{r}
# unique species in the clean list
  OrdwaySpeciesNames %>%
  summarise(count = n_distinct(SpeciesNameCleaned))
```

### Step 2
  
```{r}
# inspect OrdwaySpeciesNames
Corrected <-
  OrdwayBirds %>%
  inner_join( OrdwaySpeciesNames ) %>% 
  select( Species = SpeciesNameCleaned, Month, Day ) %>%
  na.omit()  # cleaned up the missing ones
```
SpeciesNames is used for matching cases. Month and Day will be added.


### Step 3

We want to identify the top 5-6 bird species sighted at the Katherine Ordway Natural History Study Area.

```{r}
# count sightings by species in descending order
  Corrected %>% 
  group_by(Species) %>% 
  summarise(count=n()) %>%
  arrange(desc(count))
# a hint on p.164 recommends displaying the top 10 species to choose our threshold

```

```{r}
# define a sightings threshold; produce a table with only birds belonging to major species
Major <-
Corrected %>% 
  group_by(Species) %>% 
  summarise(count=n()) %>%
  arrange(desc(count)) %>%
  head(6) %>%
.$Species

Majors <-
  Corrected %>% 
  filter(Species %in% Major)

Majors
```


### Step 4

We now want to produce a month-by-month count for each of the major species, and then construct a chart to tell the story of what time of year the various species appear.

```{r}
# prepare glyph-ready data table called `ByMonth`
ByMonth <- Majors %>%
  group_by(Species, Month) %>%
  summarise(count = n()) %>%
  arrange(Month)
```


```{r}
# ggplot command
ggplot(ByMonth) +
  aes(x = Month, weight = count) +
  geom_bar(fill = "#112446") +
  theme_bw() +
  facet_wrap(vars(Species))
```

According to the graph, we can answer the questions posed:

##### 1. Which species are present year-round?  
American Goldfinch and Black-capped chickadee


##### 2. Which species are migratory, that is, primarily present in one or two seasons?
Lincolns Sparrow and Slate-colored Junco


##### 3. What is the peak month for each major species? (bullet list)
* American Goldfinch: October
* Black-capped Chickadee: November 
* Field Sparrow: May
* Lincolns Sparrow: October 
* Slate-colored Junco: October 
* Tree swallow: March


##### 4. Which major species are seen in good numbers for at least 6 months of the year?
American Goldfinch Black-capped Chickadee Tree swallow


