---
title: "Activity: Popular Names"
author: "Ziyuan Ye"
date: "October 4 2021"
output: html_notebook
---



# Set Up

```{r}
# load necessary packages
library(tidyverse)
library(mosaic)
library(dcData)
```


```{r}
# Load the BabyNames data into RStudio environment (from dcData package)
data("BabyNames")

```

# Activity

**Goal**: By the end of the activity, each person will create a graph showing ups and downs in the popularity of four names according to the U.S. social security administration  


### Step 1
The case is the number of baby name occured, variables are: name, sex, count, and year.


### Step 3
The glyph-ready data table should consist of all the variables. “Popularity” is a new variable by certain name count in the certain year. “Popularity” is the y-axis, "year" is the x-axis. “name” variable is an aesthetic for the legend.

* “sex” and “count” does not appear in the graph 
* “Popularity” is similar to ’count"

### Step 4



### Step 5



### Step 7: modify the starter code given in the book to produce your own R code..





