---
title: "STAT 184 Homework Exercises"
subtitle: "DataComputing Chapters 7"
author: "Ziyuan Ye "
output: html_notebook
---

## Assigned Exercises

- DC Chapter 7 Exercises: 7.1, 7.3, 7.5, 7.6, 7.7, 7.8


## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
library(dplyr)
library(esquisse)
library(ggplot2)
```

## Chapter 7 Exercises

### Problem 7.1

1.
transformation function
2.
transformation function
3.
reduction function
4.
transformation function
5.
transformation function
6.
reduction function
7.
transformation function
8.
reduction function


### Problem 7.3
1.
```{r}
Minneapolis2013=(Minneapolis2013)
Minneapolis2013 %>%
  summarise(count = n())
```

2.
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  top_n(5)
```

3.
*
```{r}
Minneapolis2013 %>% 
  group_by(First) %>%
  summarise(count = n()) %>%
  filter(First=="undervote")
```

*
```{r}
Minneapolis2013 %>% 
  group_by(Second) %>%
  summarise(count = n()) %>%
  filter(Second=="undervote")
```

*
```{r}
Minneapolis2013 %>% 
  group_by(Third) %>%
  summarise(count = n()) %>%
  filter(Third=="undervote")
```


4.
```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  top_n(3)
```

5.
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  top_n(3)
```
P-06, 9711 ballots


### Problem 7.5

a.
```{r}
VoterData_A <-
  Minneapolis2013 %>%
  group_by(First, Second)
```
The voterData has been modified by First and Second, case is voter

b.
```{r}
VoterData_B <-
 Minneapolis2013 %>%
  summarise( total = n() )
```
It represent the total number of case in VoterData_B

c.
```{r}
VoterData_C <-
  Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise( total = n() )
```
It represent the total number of First and Second cases correspondingly

d.
After summarise( total = n() ) %>%, the result is an int, there is no First or Second.


### Problem 7.6: 

1.
```{r}
ZipGeography = (ZipGeography)
ZipGeography %>%
 filter(!(Timezone %in% " ") | is.na(Timezone)) %>%
 ggplot() +
 aes(x = Population, y = LandArea) +
 geom_point(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(State))
```

2.
```{r}
new_ZipGeography <-
  ZipGeography %>%
  group_by(State) %>%
  summarise(sum_population = sum(Population, na.rm = TRUE) )
```

```{r}
mUSMap(new_ZipGeography, key = "State", fill = "sum_population")
```



3.
```{r}
noval_ZipGeography <-
  ZipGeography %>%
  group_by(State) %>%
  summarise(unit_area_state = (sum(LandArea, na.rm = TRUE) /sum(Population, na.rm = TRUE)) )
```

```{r}
mUSMap(noval_ZipGeography, key = "State", fill = "unit_area_state")
```


### Problem 7.7: 

a. 
number and average age of female and male patient

b.
for each diagnosis result, number of patient in it and average age

c.
diagnosis: for female and male, each diagnosis result, number of patient in it and average age

d.
diagnosis: for eacha ge of patient,each diagnosis result, number of patient in it and average age

e.
number of each age patient, average age



### Problem 7.8: 

1.
```{r}
ZipDemography=(ZipDemography)
ggplot(ZipDemography) +
 aes(x = Foreignborn, y = SpeakalanguageotherthanEnglishathome5yearsandover) +
 geom_point(size = 1L, colour = "#0c4c8a") +
 labs(y = "foreign_language") +
 theme_minimal()

```


2.
Set Bachelorsdegreeorhigher be the y-axis, total population be the x-axis. The coefficient of slope is the fraction of people who has bachelors degree or higher, then add state as facet.






