---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 15"
author: "Ziyuan Ye"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 15 Exercises:  15.1, 15.2, 15.3, 15.4, 15.5  

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(esquisse)
library(lubridate)
library(dcData)
data(CPS85)
data(BabyNames)
data(Galton)
```



## Chapter 15 Exercises

### Problem 15.1
```{r}
ggplot(CPS85) +
 aes(x = sex, y = wage, fill = sex) +
 geom_boxplot() +
 scale_fill_hue() +
 theme_bw()
```


### Problem 15.2
1. Most NCHS people height are 1.65m
2. Most NCHS female height is 1.6m, male height is 1.75m
3. The estimated BMI for 40-year old people is 25. The estimated BMi for 70 years people is 27.5.


### Problem 15.3
```{r}
ggplot(CPS85) +
 aes(x = educ, y = wage, colour = sex) +
 geom_point(size = 1L) +
 geom_smooth()+
 scale_color_hue() +
 ylim(0,15)+
 theme_bw()
```

### Problem 15.4
```{r}
ggplot(Galton)+
  aes(x=height,y=mother)+
  geom_density_2d()+
  facet_wrap(vars(sex)) +
  theme_bw()
```

### Problem 15.5

1. no, we have the information that from the graph, zip codes with over 65 population tend to have less high child population. 
2. the data is consistent

1. no, the flat line does not consistent with the data. From statistical theory, more sample size shorter the width of Confidence interval. 
2. 20 sample: 80 sample is 2:1 
3. Yes, the graph matchs the equation







