---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 11"
author: "Ziyuan Ye "
output: html_notebook
---

## Assigned Exercises

- DC Chapter 11 Exercises: 11.2, 11.3, 11.5, 11.6  


## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
library(esquisse)
data (ZipDemography)
data (ZipGeography)
data(healthIndicator)

```



## Chapter 11 Exercises

### Problem 11.2
There is no column is same in both tables.The rows of each table is different. By simply copying long and lat value will be incorrect information.



### Problem 11.3
1. 
2.
3.
```{r}
crowed <-
  ZipGeography %>%
  select(ZIP, Latitude, Longitude)%>%
  filter("Population" > 50000)
```

```{r}
ggplot(crowed) +
  aes(x = Latitude, y = Longitude) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  theme_bw()
```


4.
i. 
```{r}
  ZipGeography %>%
  left_join(ZipDemography) %>%
  group_by(State) %>%
  summarise(sum(Vacanthousingunits, na.rm = TRUE) / sum(Totalhousingunits, na.rm = TRUE) )
```

ii.
```{r}
  ZipGeography %>%
  left_join(ZipDemography) %>%
  group_by(State) %>%
  summarise(sum(X65yearsandover, na.rm = TRUE)/sum(Population, na.rm = TRUE) )
```

iii.
```{r}
  ZipGeography %>%
  left_join(ZipDemography) %>%
  group_by(State) %>%
  summarise(sum(Bachelorsdegreeorhigher, na.rm = TRUE)/sum(Population, na.rm = TRUE) )
```


5.
```{r}
new_crowed <-
  ZipGeography %>%
  left_join(ZipDemography) %>%
  mutate(fraction = sum(X65yearsandover, na.rm = TRUE)/sum(Population, na.rm = TRUE))%>%
  arrange(Population, na.rm = TRUE)%>%
  select(ZIP, Latitude, Longitude, fraction)%>%
  head(10000)
```

```{r}
ggplot(new_crowed) +
  aes(x = Latitude, y = Longitude, colour = fraction) +
  geom_point(shape = "circle", size = 1.5) +
  scale_color_gradient() +
  theme_bw()
```


6.
```{r}
new_crowed2 <-
  ZipGeography %>%
  left_join(ZipDemography) %>%
  filter(WaterArea > 1.5 * LandArea)%>%
  select(ZIP, Latitude, Longitude, Population)
```

```{r}
ggplot(new_crowed2) +
  aes(x = Latitude, y = Longitude, colour = Population) +
  geom_point(shape = "circle", size = 1.5) +
  scale_color_gradient() +
  theme_bw()
```


### Problem 11.5
1.
```{r}
ZipDemography %>%
  summarise(count = n_distinct(Countries))
```

2.
```{r}
ZipGeography %>%
  left_join(ZipDemography) %>%
  group_by(CityName) %>% 
  summarise(count=n())%>%
  arrange(desc(count))
```

3.
```{r}
StatePopulation <-
ZipGeography %>%
  group_by(State) %>% 
  summarise(State_population = sum(Population, na.rm = TRUE))
```

```{r}
ZipGeography %>%
  left_join(StatePopulation) %>%
  filter(Population > 0.05 * State_population)%>%
  select(ZIP,CityName)
```

4.
```{r}
ZipGeography %>%
  group_by(State,Timezone)%>%
  summarise()
```

5.
```{r}
ZipGeography %>%
  group_by(State,CityName,Timezone)%>%
  summarise()
```

6.
```{r}
ZipGeography %>%
  group_by(State,County,Timezone)%>%
  summarise()
```


### Problem 11.6
```{r}
healthIndicator <- dcData::CountryData
```

1.
Using left join on (countryB = origincode, countryA = destcode, Y2000 = toAfromB)

2.
Using left join on (countryA = destcode, countryB = origincode, Y2000 = toAfromB)

3.
Using left join on (countryA = iso_a3, infantA = infant)

4.
Using left join on (countryB = iso_a3, infantB = infant)









