---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 13 & 16"
author: "Ziyuan Ye"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 13 Exercises:  13.1, 13.2, 13.3
- DC Chapter 16 Exercises:  16.1, 16.2

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(esquisse)
library(lubridate)
library(dcData)
data(BabyNames)
```



## Chapter 13 Exercises

### Problem 13.1
```{r}
BabyNames %>% 
  group_by(sex,name) %>%
  summarise(total = sum(count)) %>%
  filter(rank(desc(total)) <= 5) 
```


### Problem 13.2
1.
```{r}
Table1<-
BabyNames%>% 
  group_by(year,name) %>%
  summarise(YearCount = sum(count))%>%
  mutate(Rank = rank(desc(YearCount)),
         ranking = ifelse(Rank <=100, "Top_100","Below"))
```

```{r}
Table1Plus<-
Table1%>%
  group_by(year,ranking)%>%
  summarise(total = sum(YearCount))%>%
  arrange(desc(year))
Table1Plus
```


2.
```{r}
Table2<-
  Table1Plus%>%
  pivot_wider(names_from=ranking,values_from = total)%>%
  mutate(ratio = (Top_100)/(Top_100+Below))
Table2
```


3.
```{r}
ggplot(Table2) +
 aes(x = ratio, y = year) +
 geom_point(size = 1L, colour = "#0c4c8a") +
  labs(x = ' fraction of babies in the top 100', title = ' Fraction of babies with names in the top 100 each year.')+
 theme_bw()
```


### Problem 13.3
```{r}
PopularName<-
BabyNames %>% 
  group_by(year,name) %>%
  summarise(YearCount = sum(count)) %>%
  mutate(Rank = rank(desc(YearCount)),
         ranking = ifelse(Rank <=50, "very popular",ifelse(Rank >=1000,"very unpopular","normal")))
PopularName
```

```{r}
VeryPopularName <-
  PopularName %>%
  filter(ranking == 'very popular') %>%
  select(name)
```

```{r}
VeryunPopularName <-
  PopularName %>%
  filter(ranking == 'very unpopular') %>%
  select(name)
```

```{r}
specialName<-
  VeryPopularName%>%
  inner_join(VeryunPopularName, by=c("name"="name")) %>%
  distinct(name) %>%
  select(name)
specialName
```

## Chapter 16 Exercises


### Problem 16.1
1.
```{r}
lubridate::mdy("April 30, 1777")
```

```{r}
difftime("2000-12-18",lubridate::mdy("April 30, 1777"),units = "days")
```

2.
```{r}
lubridate::mdy("06-23-1912")
```

```{r}
difftime("2000-12-18",lubridate::mdy("06-23-1912"),units = "days")
```

3.
```{r}
lubridate::dmy("3 March 1847")
```

```{r}
difftime("2000-12-18",lubridate::dmy("3 March 1847"),units = "days")
```

4.
```{r}
lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am")
```

```{r}
difftime("2000-12-18",lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am"),units = "days")
```

5.
```{r}
lubridate::mdy("July 20, 1969")
```

```{r}
difftime("2000-12-18",lubridate::mdy("July 20, 1969"),units = "days")
```


### Problem 16.3
1.
“42,659.30” only readr::parse_number()

2.
“17%” only readr::parse_number() 

3.
“Nineteen” neither 

4.
“£100” only readr::parse_number() 

5.
“9.8 m/seconds-square” only readr::parse_number() 

6.
“9.8 m/s^2” only readr::parse_number() 

7.
“6.62606957 × 10^-34 m2 kg / s” neither 

8.
“6.62606957e-34” both 

9.
“42.659,30” (A European style) only readr::parse_number()
