---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 18"
author: "Ziyuan Ye"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 18 Exercises:  18.1, 18.2

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
data(NCHS)

```



## Chapter 18 Exercises

### Problem 18.1
1.
living_areas, fireplaces, bathroom

2.
No, it doesn't matter

3.
The price of house with more than one bathroom(151424.497$) is larger than house with one bathroom(179796.647)

4.
When living area is greater than 2816 feet, the number of firespace matters the price. More fireplaces lead to higher price.

### Problem 18.2
```{r}
NCHS %>%
  na.omit() %>%
  nrow()
```

```{r}
CompleteCases <- 
  NCHS %>%
  select(diabetic, weight, age, bmi, chol, smoker) %>%
  na.omit() 
```

1.
```{r}
library(party)
mod2 <- party::ctree(diabetic ~ weight + age + bmi, data = CompleteCases)
```

2.
```{r}
plot(mod2, type = "simple")
```

```{r}
CompleteCases %>%
  mutate(probability = as.numeric(predict(mod2)), 
         likelihood = ifelse(diabetic, probability, 1-probability)) %>%
  summarise(log_likelihood = sum(log(likelihood)))
```

3.
The patient whose age is less than 49 and whose bmi is greater than 35.349 has the highest risk of getting diabetes

4.
The patient whose age is less than 49 and whose bmi is less than 23 has the lowest risk of getting diabetes

