---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 12"
author: "Ziyuan Ye"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 12 Exercises:  12.1, 12.2, 12.3, 12.4 


## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
data(BabyNames)
```



## Chapter 12 Exercises


### Problem 12.1

1.
```{r}
BothSexes <-
  BabyNames %>%
  pivot_wider(names_from = sex, values_from = count)%>%
  filter(M > 5 | F > 5)
BothSexes
```

2.
```{r}
CLosest_Balance<-
  BothSexes %>%
  group_by(name) %>%
  summarise(balance=abs(log(F / M)))%>%
  arrange(balance)%>%
  head(10)
CLosest_Balance
```

3.
```{r}
CLosest_Balance_100babys<-
  BothSexes %>%
  group_by(name) %>%
  filter(M > 100, F > 100)%>%
  summarise(balance=abs(log(F / M)))%>%
  arrange(balance)%>%
  head(10)
CLosest_Balance_100babys
```

4.
```{r}
CLosest_Balance_Popularity<-
  BothSexes %>%
  group_by(name) %>%
  filter(M + F > 100)%>%
  summarise(balance=abs(log(F / M)))%>%
  arrange(balance)%>%
  head(10)
CLosest_Balance_Popularity
```

5.
```{r}
CLosest_Balance_Switch<-
  BothSexes %>%
  group_by(name,year) %>%
  summarise(F_ratio = F / (F+M), M_ratio = M / (F+M))
CLosest_Balance_Switch
```



### Problem 12.2

1.
* version1: The number of babies names “Ida, Robert, Theresa” separated by sex in 1912 and 2012.

* version2: The number of female and male whose name is “Ida, Robert, Theresa” born in 1912 and 2012.

* version3: The number of female born in 1912 and 2012, and the number of male born in 1912 and 2012.

2.
```{r}
Version2<-
BabyNames %>% 
  filter(name == "Ida"|name =="Robert"|name =="Theresa", year == 2012|year==1912) %>%
  group_by(name, sex, year) %>% 
  summarise(nbabies = sum(count))%>%
  pivot_wider(names_from = sex, values_from = nbabies, values_fill = NA)
Version2
```
Version2 is wider with female and male column. By adding pivot_wider(names_from = sex, values_from = nbabies, values_fill = NA) to convert version1 to version2.

3.
```{r}
Version3<-
BabyNames %>% 
  filter(name == "Ida"|name =="Robert"|name =="Theresa", year == 2012|year==1912) %>%
  group_by(name, sex, year) %>% 
  summarise(nbabies = sum(count))%>%
  pivot_wider(names_from = year, values_from = nbabies, values_fill = NA)
Version3
```
Version3 is wide with column year 1912 and 2012.Calculate the female with name “Ida, Rovert, or Therasa” borned in 1912, and 2012 separably. And males. Add R chain. pivot_wider(names_from = year, values_from = nbabies, values_fill = NA)

4.
Version2 is better. Female, male, and year are variables in version2. It is easier to calculate.

5.
I should convert version1 to version2 first, then calculate the ratio. Using proper table to calculate saving time and more tidy.


### Problem 12.3

1.
* A is wider because A stores every single country as an attribute.
* B is wider because B stores every single year as an attribute.
* They are the same "wider" with different name_from.

2.
Table B. Using data verb summarise( change = Y2000 - Y2001).

3.
Table C. Firstly join two tables by country. Then using group_by(continent ,year) and summarise(sum = sum(value)).


### Probelm 12.4

1.
In a narrow form, we have to store many redundant data, which is less useful for practical purpose because we might need write others data verbs before.

2.
BP_wide %>% mutate(change = after - before)%>% pivot_longer(cols = c(before,after),names_to = “when”, values_to = “sbp”).
In this R chain, we can clearly find out the sbp difference before and after.