---
title: "HELPrct (Data Verbs) Activity"
author: "Ziyuan Ye"
date: "Put the due date here"
output: html_notebook
---


## Set Up:

```{r}
# load packages
library(tidyverse)  # for data verbs like `group-by()` & `summarise()`
library(mosaicData) # includes `HELPrct` data set 
library(mosaic)     # includes `mplot()` interactive plot builder
library(esquisse)   # includes `esquisser()` interactive plot builder


# Load the HELPrct data from `mosaicData` into our RStudio environment
data("HELPrct", package = "mosaicData")

```


## Data Description

*TASK 1: Write a couple of sentences describing the `HELPrct` data--What is the setting for the data? What are they about?* 
The dataset represents 453 cases of observation of adult inpatients recruited from a detoxification unit. Patients with no primary care physician were randomized to receive a multidisciplinary assessment and a brief motivational intervention or usual care, with the goal of linking them to primary medical care.

## Basic Summaries with `summarise()` 

*TASK 2: Produce an expression involving `summarize()` and `HELPrct` that will produce the following.*

1. *number of people (cases) in `HELPrct` study*
2. *combined total number of times in the past 6 months all the people in `HELPrct` entered a detox program (measured at baseline)* 
3. *mean time (in days) to first use of any substance post-detox for all the people in `HELPrct`*

1.
```{r}
HELPrct %>%
  summarise(count = n())
```
2.
```{r}
HELPrct %>%
  summarise(sum_times = sum(e2b, na.rm = TRUE))
```
3.
```{r}
HELPrct %>%
  summarise(mean_times = (sum(anysubstatus, na.rm = TRUE) / n() ))
```

## Subgrouping with `group_by()` 

*TASK 3: Repeat task 2 above, but calculate the results group-by-group.  Show your code and write a sentence or two about what you observe in the results for each of the following:* 

1. *males versus females*

```{r}

```


2. *homeless or not*

```{r}

```

3. *substance*

```{r}

```

4. *break down the homeless versus housed further, by sex*

```{r}

```

5. *break down the homeless versus housed further, by substance*

```{r}

```


## TASK 4:

*Include one or more interesting plots of the data involving at least 3 variables per plot. Write a few sentences to explain the story that your plot tells about these data.  You can use one of the relationships that you studied in Task 2, or you can explore a different group of variables in the `HELPrct` that show something interesting.*  



```{r}

```


